---
title: "Procurement Survey Analytics"
author: "Preethi G"
date: "04/03/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

We shall briefly analyse the results so far from the procurements capabilties survey. 

```{r read file}
library(tidyr)
library(dplyr)
library(data.table)
library(plot)
 
survey <- read.csv ("2021-03-04_21 23 01_survey__pu.csv", row.names = NULL,
                                stringsAsFactors = FALSE)

##seperate the third column by comma spaces
survey <- survey %>% separate (X2..What.do.you.think.is.the.biggest.problem.within.public.procurements.in.India., c("A","B","C","D","E"), sep=",")
##Create list of columns to subset
newvar <- c("A","B","C","D","E")
#Subset table
problem <- survey[newvar]
problem$A <- trimws(problem$A)
problem$B <- trimws(problem$B)
problem$C <- trimws(problem$C)
problem$D <- trimws(problem$D)
problem$E <- trimws(problem$E)
#Make vector
problem_vec <- unlist(problem)
#make new table
problem_table <- table(problem_vec)
pie(problem_table)
```
According to this pie-chart, the two major problems in public procurement right now are inefficiency and corruption. 
Now we can see the distribution of the experience in public procurements of people responding to this survey
```{r pressure}
library(ggplot2)
##Since the survey was changed after a few responses, we will first normalize the data available
survey <- data.frame(lapply(survey, function(x) {
                gsub("Less than 6 months", "I am not familiar with public procurement data", x)}))

survey <- data.frame(lapply(survey, function(x) {
                gsub("1 - 2 years", "I occasionaly work with public procurement data", x)}))

survey <- data.frame(lapply(survey, function(x) {
                gsub("More than two years", "I regularly work with and analyze public procurement data", x)}))

counts <- table(survey$X1.How.familiar.are.you.with.public.procurement.data.)

g <- ggplot(survey, aes(X1.How.familiar.are.you.with.public.procurement.data.)) + geom_bar() +theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
g
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
