---
title: "Procurement Survey Analytics"
author: "Preethi G"
date: "04/03/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

We shall briefly analyse the results so far from the procurements capabilties survey. 

```{r read file}
library(tidyr)
library(dplyr)
library(data.table)

 
#survey <- read.csv ("2021-03-04_21 23 01_survey__pu.csv", row.names = NULL,
 #                               stringsAsFactors = FALSE)

survey <- read.csv ("2021-03-05_22 08 34_survey__pu.csv", row.names = NULL,
                                stringsAsFactors = FALSE)


##seperate the third column by comma spaces
survey <- survey %>% separate (X2..What.do.you.think.is.the.biggest.problem.within.public.procurements.in.India., c("A","B","C","D","E"), sep=",")
##Create list of columns to subset
newvar <- c("A","B","C","D","E")
#Subset table
problem <- survey[newvar]
problem$A <- trimws(problem$A)
problem$B <- trimws(problem$B)
problem$C <- trimws(problem$C)
problem$D <- trimws(problem$D)
problem$E <- trimws(problem$E)
#Make vector
problem_vec <- unlist(problem)
#make new table
problem_table <- table(problem_vec)
pie(problem_table)
```
According to this pie-chart, the two major problems in public procurement right now are inefficiency and corruption. 
Now we can see the distribution of the experience in public procurements of people responding to this survey
```{r experience}
library(ggplot2)
##Since the survey was changed after a few responses, we will first normalize the data available
survey <- data.frame(lapply(survey, function(x) {
                gsub("Less than 6 months", "I am not familiar with public procurement data", x)}))

survey <- data.frame(lapply(survey, function(x) {
                gsub("1 - 2 years", "I occasionaly work with public procurement data", x)}))

survey <- data.frame(lapply(survey, function(x) {
                gsub("More than two years", "I regularly work with and analyze public procurement data", x)}))

counts <- table(survey$X1.How.familiar.are.you.with.public.procurement.data.)

g <- ggplot(survey, aes(X1.How.familiar.are.you.with.public.procurement.data.)) + geom_bar() +theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

g
```

Now we will look at what the problems with the data are
```{r data}
library(ggplot2)
##separate the third column by comma spaces
survey <- survey %>% separate (X3..What.is.the.biggest.challenge.you.face.while.working.with.public.procurement.data., c("A","B","C","D","E"), sep=",")

##Create list of columns to subset
newvar <- c("A","B","C","D","E")
#Subset table
problem <- survey[newvar]

problem$A <- trimws(problem$A)
problem$B <- trimws(problem$B)
problem$C <- trimws(problem$C)
problem$D <- trimws(problem$D)
problem$E <- trimws(problem$E)
#Make vector
problem_vec <- unlist(problem)
#make new table
problem_table <- data.frame(table(problem_vec))

g <- ggplot(problem_table, aes(x = problem_vec, y = Freq)) + geom_bar(stat = "identity") +theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
g

```
Now we will look at what kind of analytics is most preferred 
```{r analytics}
library(ggplot2)
##separate the third column by comma spaces
survey <- survey %>% separate (X5..What.kind.of.analytics.would.you.like.to.see.within.public.procurements, c("A","B","C","D","E"), sep=",")

##Create list of columns to subset
newvar <- c("A","B","C","D","E")
#Subset table
problem <- survey[newvar]

problem$A <- trimws(problem$A)
problem$B <- trimws(problem$B)
problem$C <- trimws(problem$C)
problem$D <- trimws(problem$D)
problem$E <- trimws(problem$E)
#Make vector
problem_vec <- unlist(problem)
#make new table
problem_table <- data.frame(table(problem_vec))

g <- ggplot(problem_table, aes(x = problem_vec, y = Freq)) + geom_bar(stat = "identity") +theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
g

```

How can we make your life easier

```{r analytics}
library(ggplot2)
##separate the third column by comma spaces
survey <- survey %>% separate (X4..How.can.we.make.your.life.easier.while.working.with.public.procurement.data., c("A","B","C","D","E"), sep=",")

##Create list of columns to subset
newvar <- c("A","B","C","D","E")
#Subset table
problem <- survey[newvar]

problem$A <- trimws(problem$A)
problem$B <- trimws(problem$B)
problem$C <- trimws(problem$C)
problem$D <- trimws(problem$D)
problem$E <- trimws(problem$E)
#Make vector
problem_vec <- unlist(problem)
#make new table
problem_table <- data.frame(table(problem_vec))

g <- ggplot(problem_table, aes(x = problem_vec, y = Freq)) + geom_bar(stat = "identity") +theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
g

library(ggplot2)
##separate the third column by comma spaces
survey <- survey %>% separate (X5..What.kind.of.analytics.would.you.like.to.see.within.public.procurements, c("A","B","C","D","E"), sep=",")

##Create list of columns to subset
newvar <- c("A","B","C","D","E")
#Subset table
problem <- survey[newvar]

problem$A <- trimws(problem$A)
problem$B <- trimws(problem$B)
problem$C <- trimws(problem$C)
problem$D <- trimws(problem$D)
problem$E <- trimws(problem$E)
#Make vector
problem_vec <- unlist(problem)
#make new table
problem_table <- data.frame(table(problem_vec))

g <- ggplot(problem_table, aes(x = problem_vec, y = Freq)) + geom_bar(stat = "identity") +theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
g

```

```{r capacity build}

counts <- table(survey$X7..Would.you.be.interested.in.a.workshop.on.the.use.of.public.procurement.data.)

g <- ggplot(survey, aes(X7..Would.you.be.interested.in.a.workshop.on.the.use.of.public.procurement.data.)) + geom_bar() +theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

g

library(ggplot2)
##separate the third column by comma spaces
survey <- survey %>% separate (X8..If.we.were.to.do.a.capacity.building.workshop.around.public.procurement.data..what.would.you.find.most.useful., c("A","B","C","D","E"), sep=",")

##Create list of columns to subset
newvar <- c("A","B","C","D","E")
#Subset table
problem <- survey[newvar]

problem$A <- trimws(problem$A)
problem$B <- trimws(problem$B)
problem$C <- trimws(problem$C)
problem$D <- trimws(problem$D)
problem$E <- trimws(problem$E)
#Make vector
problem_vec <- unlist(problem)
#make new table
problem_table <- data.frame(table(problem_vec))

g <- ggplot(problem_table, aes(x = problem_vec, y = Freq)) + geom_bar(stat = "identity") +theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
g

```
Areas of interest

```{r capacity build}

library(ggplot2)
##separate the third column by comma spaces
survey <- survey %>% separate (X12..Please.choose.upto.3.topics.of.interest.for.you, c("A","B","C","D","E"), sep=",")

##Create list of columns to subset
newvar <- c("A","B","C","D","E")
#Subset table
problem <- survey[newvar]

problem$A <- trimws(problem$A)
problem$B <- trimws(problem$B)
problem$C <- trimws(problem$C)
problem$D <- trimws(problem$D)
problem$E <- trimws(problem$E)
#Make vector
problem_vec <- unlist(problem)
#make new table
problem_table <- data.frame(table(problem_vec))

g <- ggplot(problem_table, aes(x = problem_vec, y = Freq)) + geom_bar(stat = "identity") +theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
g

```